### 2021-02-22 architecture.tex
Architecture: Disable typesetting the WIP sections
Add some todos
S > C_2

The recommender consists of modules that perform specific subtasks,
each of which is described in detail in one of the following sections (see also \cref{fig:architecture}):
\begin{enumerate}
\item Graphifier converts the input \gls{cnf} problem into a problem graph.
\item \Gls{gcn} converts a problem graph into symbol embeddings.
\todo{MS: Kdyz embeddingy nebudou v preliminaries, je asi OK ctenare, ktery by o nich neslysel, zde trochu vydesit.
Ale v te prislusne podsekci tim zas zacit.}
\item An output function \cite{Zhou2018} converts the symbol embeddings into a vector of symbol costs.
\todo{MS: ``output function \cite{Zhou2018}'' my nic nerika, mel bych to znat?\\
FB: Zhou2018 je review GNNs. Output function je termin, ktery se tam pouziva. Ta citace je nejspis tady nepotrebna.}
\item Ranking converts the symbol costs into a symbol precedence.
It is only used in generating mode.
\item Loss function converts the symbol costs and a pair of precedences into a loss value.
It is only used in training mode.
\end{enumerate}
\todo{MS: tohle zatim chapu jako predbezny nastrel. Leda by uz pred tim bylo vysvetleno:
embedding, \gls{gcn}/convolution layers, ... \\
FB: Staci predestrit, ze detaily vysvetlim pozdeji? MS: asi jo :)}

@@

@@

Let $(P, \PrecBetter, \PrecWorse)$ be a training example ($\Better{\PrecBetter}{\PrecWorse}{P}$).
The precedence cost classifies this example correctly if $C(\PrecBetter) < C(\PrecWorse)$,
or alternatively $C_2(\PrecBetter, \PrecWorse) = C(\PrecWorse) - C(\PrecBetter) > 0$.
% We have positive C_2 score for correctly predicted examples.
% The loss function transorms that into a loss value close to 0.
We approach this problem as an instance of binary classification with the logistic loss \cite{Mohri2018}:
% p. 128
\todo{MS: First mention of a ``binary classifier''!
We classify the examples, sure, but you did not say it yet.}
\begin{align*}
L(P, \PrecBetter, \PrecWorse)
&= - \log \sigmoid C_2(\PrecBetter, \PrecWorse)
%&= - \log \sigmoid (C(\PrecBetter) - C(\PrecWorse)) \\
%&= - \log \sigmoid \sum_{i=1}^n i (c(\PrecBetter(i)) - c(\PrecWorse(i)))
\end{align*}

Note that the classifier cannot simply train $C_2$ to output a negative number on all pairs of precedences,
because $C_2$ is a difference of two precedence costs.
By training on the example $(P, \PrecBetter, \PrecWorse)$,
we are effectively pushing $C(\PrecBetter)$ down and $C(\PrecWorse)$ up.

@@

\newcommand{\Solver}{S}
\newcommand{\SolverRun}[2]{\Solver(#1, #2)}

>>>>

The recommender consists of modules that perform specific subtasks,
each of which is described in detail in one of the following sections (see also \cref{fig:architecture}):
\begin{enumerate}
\item Graphifier converts the input \gls{cnf} problem into a problem graph.
\item \Gls{gcn} converts a problem graph into symbol embeddings.
\todo{MS: Kdyz embeddingy nebudou v preliminaries, je asi OK ctenare, ktery by o nich neslysel, zde trochu vydesit.
Ale v te prislusne podsekci tim zas zacit.}
\item An output function \cite{Zhou2018} converts the symbol embeddings into a vector of symbol costs.
\todo{MS: ``output function \cite{Zhou2018}'' my nic nerika, mel bych to znat?\\
FB: Zhou2018 je review GNNs. Output function je termin, ktery se tam pouziva. Ta citace je nejspis tady nepotrebna.}
\item Ranking converts the symbol costs into a symbol precedence.
It is only used in generating mode.
\todo{FB: Define ranking.}
\item Loss function converts the symbol costs and a pair of precedences into a loss value.
It is only used in training mode.
\end{enumerate}
\todo{MS: tohle zatim chapu jako predbezny nastrel. Leda by uz pred tim bylo vysvetleno:
embedding, \gls{gcn}/convolution layers, ... \\
FB: Staci predestrit, ze detaily vysvetlim pozdeji? MS: asi jo :)}

@@

\todo[inline]{FB: Define ranking and argsort.}

@@

Let $(P, \PrecBetter, \PrecWorse)$ be a training example ($\Better{\PrecBetter}{\PrecWorse}{P}$).
The precedence cost classifies this example correctly if $C(\PrecBetter) < C(\PrecWorse)$,
or alternatively $S(\PrecBetter, \PrecWorse) = C(\PrecWorse) - C(\PrecBetter) > 0$.
% We have positive S score for correctly predicted examples.
% The loss function transorms that into a loss value close to 0.
We approach this problem as an instance of binary classification with the logistic loss \cite{Mohri2018}:
% p. 128
\todo{MS: First mention of a ``binary classifier''!
We classify the examples, sure, but you did not say it yet.}
\begin{align*}
L(P, \PrecBetter, \PrecWorse)
&= - \log \sigmoid S(\PrecBetter, \PrecWorse)
%&= - \log \sigmoid (C(\PrecBetter) - C(\PrecWorse)) \\
%&= - \log \sigmoid \sum_{i=1}^n i (c(\PrecBetter(i)) - c(\PrecWorse(i)))
\end{align*}

Note that the classifier cannot simply train $S$ to output a negative number on all pairs of precedences,
because $S$ is a difference of two precedence costs.
By training on the example $(P, \PrecBetter, \PrecWorse)$,
we are effectively pushing $C(\PrecBetter)$ down and $C(\PrecWorse)$ up.

@@
